  \documentclass{amsart}
	\usepackage{amssymb,latexsym}
	\usepackage{verbatim} 
\author{shaun yi cheng}
\begin{document}
\textbf{Lemma 2}
\emph{If the Cartesian product $X\times Y$ of Tychonoff spaces $X$ and $Y$ is pseudocompact, then the projection $\pi_X: X\times Y \rightarrow X$ transforms functionally closed subsets of $X \times Y$ to closed subsets of $X$.}
\begin{proof}
Let $X, Y$ be Tychonoff and $X\times Y$ be pseudocompact. By way of contradiction, suppose that there exists a functionally closed subset $Z$ of $X \times Y$ such that $\pi_X[Z]$ is not closed in $X$. Let $x_0\in cl_X \pi_X[Z] \backslash \pi_X[Z] \neq \emptyset$. Let $g:X\times Y \rightarrow [0,1] $ such that $Z=g^\leftarrow(0)$.

Define $f:X\times Y \rightarrow [0,1] $ such that $f(x,y)=min\{\frac{g(x,y)}{g(x_0,y)},1\}.$
By our definition, $f$ is a continuous function. Moreover, $f(x_0,y)=1 $ for all $y\in Y$ and $Z=f^\leftarrow(0)$.

Since $X$ is Tychonoff, it is first-countable. Let $\mathcal{B}_{x_0}=\{B_k \in \tau(X): 
B_0 \supset B_1 \supset B_2 \supset \cdots $ and $x_0 \in B_k, k=1,2,3,...$ \} be a neighborhood basis of $x_0$.   We shall define two sequences, $(x_0, y_{i})$ and$ (x_i,y_i)$, and their open neighborhoods(open in $X\times Y$), $V_i$'s and $W_i$'s by induction: 

Step 1:  
Pick a point in $Z$ and label it $(x_1,y_1)$. 
Since $X$ is Hausdorff and $\mathcal{B}$ is the neighborhood basis of $x_0$, there exist $V_1 \in \mathcal{B}$, and basic open sets $W_1 \in \tau(X)$ and $Y_1 \in \tau(Y)$ such that  $(x_1,y_1) \in W_1\times Y_1$ and $(x_0,y_1)\in V_1\times Y_1 $, and $W_1 \cap V_1 = \emptyset$. 

Step n: Since $x_0 \in V_{n-1}\in \mathcal{B}$ and $x_0 \in \pi_X(Z)$, we can find a
point $(x_n, y_n) \in Z$ such that $x_n \in V_{n-1}$, and that $y_n$ is chosen so that $f(x_n, y_n)=0$. 
Now, since $f$ is continuous and $\mathcal{B}$ is the neighborhood basis of $x_0$, we can take  $V_n \in \mathcal{B}$( where $V_n \subset V_{n-1}$),  and $W_n \subset V_{n-1}$, a basic open set of $X$, and $Y_n$, a basic open set of $Y$, such that $W_n \times Y_n \in \tau(X\times Y)$ and $V_n \times Y_n \in \tau(X\times Y)$ are open sets in $X\times Y$ that contains $(x_n,y_n), (x_0,y_n)$, respectively. 


After $\omega $ many steps, we've constructed infinitely $W_i$'s and $V_i$'s such that $f[W_i\times Y_i]\subseteq [0,\frac{1}{3})$ and $f[V_i\times Y_i]\subseteq (\frac{1}{3},1]$. 
Now, we will show that the family $\mathcal{F}=\{W_i\times Y_i: 1\leq i < \infty\} $ is locally finite. 
Let $(x',y')\in X\times Y$. If $(x',y')\in W_i$ for some $W_i \in \mathcal{F}$, then we are done because the sets in $\mathcal{W}$ are pair-wise disjoint. 

Suppose that $(x',y') \notin \{x_0\}\times Y$, then there must be some $V_j \in \mathcal{B}$ such that $x'\notin V_j$. Moreover, since $X$ is Hausdorff, there exist open sets $U_x\in \tau(X), V_j\in \mathcal{B}$ such that $x'\in U_x$ and $U_x$ is disjoint from $V_j$. But $W_k \subseteq V_j $ for all $k>j.$ So there can be at most $j$ many $W_i$'s such that $W_i\cap V_j'\neq \emptyset.$ Pick any open set $U_y\subset Y$ that contains $y'$. Then $U_x\times U_y \subset X\times Y$ is an open neighborhood of $(x',y')$ which only meets $\mathcal{F}$ finitely many times.


Now suppose that $(x',y') \in \{x_0\}\times Y$. Since $x'=x_0, f(x',y')=0.$ Since $f:X\times Y \rightarrow [0,1]$ is 
continuous, there exist $U\in \tau(X\times Y)$ such that $(x',y')\in U$ and $f[U]\in (\frac{2}{3},1].$ Hence, $U$ does not meet $\mathcal{F}$. Because if it does, then $f[U]\cap [0,\frac{1}{3}) \neq \emptyset,$ contradicting that $f[U]\in (\frac{2}{3},1]$. 

We've shown that the family $\mathcal{F}\subset \mathcal{P}(X\times Y)$ is locally finite. However, $\mathcal{F}$ is infinite, and this contradicts Lemma 3. Thus, $X\times Y$ cannot be pseudocompact. 






\end{proof}









\end{document}