% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Shaun Y. Cheng}
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{cheng754@gmail.com (785)979-0490 \hfill 200 Dey St. Unit\#200, Harrison, NJ 07029}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}

\begin{resume}
\section{SOFTWARE\\DEVELOPMENT} 
\begin{itemize}       
       \item Extensive professional experience with C++, STL.
       \item Solid understanding of algorithms and data structures.
       \item Working knowledge of: Java, Scala, GCP Bigtable, Pub/Sub, BigQuery.
\end{itemize}
\section{WORK \\ EXPERIENCE} 
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font         
         
		{\sl Backend Software Devoloper in R\&D} \hfill October 2016 - Present\\
		Spotify,
                New York, NY
 \begin{itemize}  
     \item Continuously improved Spotify's recommender systems(Discover Weekly and Release Radar) for execution speed and recommendation quality.
     \item Ported popular nearest neighbor libraries(HNSW, Annoy) to reduce our data pipeline job running time by 25\%+.
     \item Integrated facebook's webhook Pub/Sub into backend systems for more personalized user experiences.
	       \
\end {itemize}
		{\sl Senior Financial Software Developer in R\&D} \hfill March 2010 - January 2016\\
                Bloomberg LP,
                New York, NY 
                 \begin{itemize}  
		 \item Responsible for the full life cycle of internal market data feeds monitoring systems, including requirements definition, prototyping, proof of concept, design, interface implementation, testing and maintenance.
                 \item Designed and implemented a scalable securities mapping system for company-wide use.
		 \end {itemize}
		{\sl Actuarial Analyst} \hfill May 2007-February 2010\\
                Actuarial Resources Corporation,
                Overland Park, KS
                 \begin{itemize} 
                 \item Developed a multi-threaded C3 Phase 2 economic stochastic economic scenario generator for
                   actuarial projections.
                 \end{itemize}
                {\sl Graduate Teaching Assistant} \hfill            August 2005 - May 2007\\
                Department of Mathematics, University of Kansas 
                 \begin{itemize}
                 \item Taught algebra, and trigonometry, calculus I\&II, statistics.
                 \end{itemize} 
                {\sl Statistical Analyst Intern} \hfill             January 2007 - May 2007\\
                Laidlaw International, Inc.
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Analyzed correlation and trends for the frequency and severity of losses.
                 \end{itemize} 
\section{EDUCATION} 
		{\sl M.A., B.S. Mathematics, 2007. } University of Kansas, Lawrence, KS. GPA: 3.8  \\
		    Graduate research in point-set toppology. Thesis: goo.gl/8kxtwK
\section{CERTIFICATES} 
            KU Charles H. Ashton Scholarship, KU Math Department Merit Scholarship, SOA exams passed: P, FM, MFE. Bloomberg Advanced Technology Training Certificate. 
\section{COMPETITIONS}
         Putnam Mathematics competition(Ranked top 400 in the U.S.). Represents Bloomberg chess team since 2010. 1st Place, Division A, Athletic Bankers League NYC 2011 \& 2012. MVP of The Year Award in 2014. NYC commercial chess league 2016 champion. Disrupt NY Hackathon 2016. Consensus 2016 Hackathon BlockApps winner.
\end{resume}
\end{document}
